Spin canonical rings of log stacky curves

### 2015-11-29 curves-write-up/spin-cring.tex
curves: shorten new bib entry, delete old gorenstein rem

\todo{Remark or paragraph on Gorenstein-ness}
``Orbifold canonical curves are projectively Gorenstein''
from an old result of Kei-ichi Watanabe. The spin case
follows from projective Cohen-Macaulay which follows from
projectively normal as seen when taking the complete
space of sections.
\todo{Robin: This is probably better fit in the introduction
than background. Per the reviewer, this is the primary
interest in taking the orbifold canonical class to be in
the form that we have. However, it seems strange in the current
place that I plopped it in.}

@@

>>>>

@@

\begin{rem}
\label{rem:gorenstein}
	The log canonical ring, defined to be the direct sum of the even
	graded pieces of the log spin canonical ring, is Gorenstein. It is
	Cohen Macaulay from \cite[Example 2.5(a)]
	{watanabe:demazure-normal-graded} and then Gorenstein by
	\cite[Corollary 2.9]{watanabe:demazure-normal-graded}. In
	particular, this tells us a log spin canonical curve, the
	projectivization of a log spin canonical ring, is projectively
	Gorenstein.
\end{rem}
